---
title: "coding"
author: "Elvin Mammadov"
date: "2024-07-01"
output: html_document
---
```{r loading the packages}
# Load packages that we will use
library(lmtest)
library(ggplot2)  
library(ggcorrplot)
library(stargazer)
library(foreign)
library(xtable)
library(plm)
library(Amelia)
library(dplyr)
library(raster)
library(rpart)
library(dplyr)
library(lubridate)


library(stringr)


```



```{r loading the packages 2}
library(pacman)

pacman::p_load(
  ggplot2,
  dplyr,
  sf,
  raster,
  rnaturalearth,
 rnaturalearthdata,
 exactextractr,
 ncdf4,
 grid,
 ggspatial,
 gridExtra,
 ggrepel,
 tidygeocoder,
 rgdal,
 osrm ,
  here,
  terra,
  tidyr
)
```

















```{r initial data cleaning, include=FALSE}
#Loading our housing data for Dresden

apartment_rent <- read.csv(here("Data", "apartment_rent_dresden.csv"), header = TRUE, sep = ";")


print(apartment_rent)

#filtering only Dresden (in Ort column have word mistakes, that is why I used this function filtering starts with "dre")

apartment_rent <- apartment_rent %>% 
 filter(grepl("^dre", Ort, ignore.case = TRUE))

#For year 2015 apartment data
apartment_rent$Datum <- as.Date(apartment_rent$Datum, format = "%d.%m.%Y") #convert this column as date

apartment_rent <- subset(apartment_rent, format(Datum, "%Y") == "2015")


#checing NAs and empty values
sum(apartment_rent$Stell_Miet == "") 
sum(apartment_rent$Nutzflaech == "") 
sum(apartment_rent$Stellplatz == "") 
sum(apartment_rent$Anzahl_Ste == "") 
sum(apartment_rent$Befeuerung == "") 
sum(apartment_rent$Bemerkung == "") 
sum(apartment_rent$Wohnungsty == "") 
sum(apartment_rent$Etagenanza == "") 

#Unselecting the unnecessary columns and columns that have more NA values
 apartment_rent <- apartment_rent[, !names(apartment_rent) %in% c( "OBJECTID_1", "Join_Count", "TARGET_FID", "OBJECTID_2", "Join_Cou_1", "TARGET_F_1", "Join_Cou_2", "TARGET_F_2" , "Stell_Miet",  "Nutzflaech",   "Stellplatz" , "Anzahl_Ste" , "Baujahr", "Letzte_Mod",  "Befeuerung",  "OBJECTID", "STVdayPege", "Adresse_Ge", "Email_Kont", "Bemerkung", "SCHIsopha", "SCHIsophp", "SCHfarbwer", "l_datum", "esri_oid", "SCHanight", "SCHpnight", "SCHfnight", "l_datum_1", "esri_oid_1", "Stadtteil", "Wohnungsty", "PRICE", "Etagenanza", "Schlafzimm", "Badezimmer")]


#In our data some values inside the column mixed as character, numeric or empty, so firstly I try find how many empty values after I change this to NA and some numbers with comma to dot.(R does not understand comma as number) In the end I check the amount of empty columns with amount of NA.

# Convert for Kaltmiete
sum(apartment_rent$Kaltmiete == "") # 0

apartment_rent$Kaltmiete <- gsub(",", ".", apartment_rent$Kaltmiete)
apartment_rent$Kaltmiete <- as.numeric(apartment_rent$Kaltmiete)
sum(is.na(apartment_rent$Kaltmiete)) # 0

# Convert for Wohnflaech
sum(apartment_rent$Wohnflaech == "") # 0

apartment_rent$Wohnflaech <- gsub(",", ".", apartment_rent$Wohnflaech)
apartment_rent$Wohnflaech <- as.numeric(apartment_rent$Wohnflaech)
sum(is.na(apartment_rent$Wohnflaech)) # 0 


# Convert for Zimmer
sum(apartment_rent$Zimmer == "") # 0

apartment_rent$Zimmer <- gsub(",", ".", apartment_rent$Zimmer)
apartment_rent$Zimmer <- as.numeric(apartment_rent$Zimmer)
sum(is.na(apartment_rent$Zimmer)) # 0

# Convert for Etage
sum(apartment_rent$Etage == "") # 0

apartment_rent$Etage <- gsub(",", ".", apartment_rent$Etage)
apartment_rent$Etage <- as.numeric(apartment_rent$Etage)
sum(is.na(apartment_rent$Etage)) # 1124

missmap(apartment_rent)

#Kaltmiete (Rent)
sum(apartment_rent$Kaltmiete == "") # 1347
apartment_rent$Kaltmiete <- gsub(",", ".", apartment_rent$Kaltmiete)
apartment_rent$Kaltmiete <- as.numeric(apartment_rent$Kaltmiete)
sum(is.na(apartment_rent$Kaltmiete)) # 1347


#Convert for Wohnflaech
sum(apartment_rent$Wohnflaech == "") # 0
apartment_rent$Wohnflaech <- gsub(",", ".", apartment_rent$Wohnflaech)
apartment_rent$Wohnflaech <- as.numeric(apartment_rent$Wohnflaech)
sum(is.na(apartment_rent$Wohnflaech)) # 0 


# Convert for Zimmer
sum(apartment_rent$Zimmer == "") # 0
apartment_rent$Zimmer <- gsub(",", ".", apartment_rent$Zimmer)
apartment_rent$Zimmer <- as.numeric(apartment_rent$Zimmer)
sum(is.na(apartment_rent$Zimmer)) # 0


# Convert for Etage
sum(apartment_rent$Etage == "") # 1124
apartment_rent$Etage <- gsub(",", ".", apartment_rent$Etage)
apartment_rent$Etage <- as.numeric(apartment_rent$Etage)
sum(is.na(apartment_rent$Etage)) # 1124






```





```{r removing outliers and fixing NAs}
#removing the datas that the rent prices is NA
apartment_rent <- apartment_rent %>% 
  filter(!is.na(Kaltmiete))

#factoring the some categorical values

apartment_rent$Keller <- factor(apartment_rent$Keller, levels = c("nein", "ja"))
apartment_rent$BalkonTerr <- factor(apartment_rent$BalkonTerr, levels = c("nein", "ja"))
apartment_rent$Aufzug <- factor(apartment_rent$Aufzug, levels = c("nein", "ja"))
apartment_rent$EBK <- factor(apartment_rent$EBK, levels = c("nein", "ja"))
apartment_rent$Garten <- factor(apartment_rent$Garten, levels = c("nein", "ja"))
apartment_rent$Barrierefr <- factor(apartment_rent$Barrierefr, levels = c("nein", "ja"))
apartment_rent$Gaeste_WC <- factor(apartment_rent$Gaeste_WC, levels = c("nein", "ja"))
apartment_rent$WBS_erford <- factor(apartment_rent$WBS_erford, levels = c("nein", "ja"))



```


```{r fixing NA and removing the outliers}
# Filtering out outliers
apartment_rent <- apartment_rent %>% filter(Zimmer < 23) # logically above the 23 is not realistic, and for perfect analyzing the relationship I remove it
apartment_rent <- apartment_rent %>% filter(Wohnflaech > 0)# can not be 0 the living size
apartment_rent <- apartment_rent %>% filter(Kaltmiete >= 100) # to set 100 for min is look like more realistic


# Visualizing missing data (assuming the 'missmap' function is available)
missmap(apartment_rent)

## Fixing the NAs according to the median
sum(is.na(apartment_rent$Etage)) #941

# Separate complete and incomplete cases for 'Etage'
complete_etage <- apartment_rent[!is.na(apartment_rent$Etage), ]
incomplete_etage <- apartment_rent[is.na(apartment_rent$Etage), ]

# Train a Decision Tree model using complete cases, we predict the NAs according to the relationship of rent prices, number of rooms and etc. it is more better than to set medians or means
model_etage <- rpart(Etage ~ Kaltmiete + Zimmer + Wohnflaech, 
                     data = complete_etage, method = "anova")

# Predict the missing 'Etage' values in incomplete cases
predicted_etage <- predict(model_etage, incomplete_etage)

# Impute the predicted values back into the original dataframe
apartment_rent$Etage[is.na(apartment_rent$Etage)] <- predicted_etage
apartment_rent$Etage <- as.integer(apartment_rent$Etage)


```

```{r loading the raster data for N02 emission in 2015}

no <- raster(here("Data" , "2015_final_1km.tif"))

crs(no) <- "+proj=longlat +datum=WGS84 +no_defs"



```








```{r}
#openning the germany map
ger_4 <- st_read(here("Data", "gadm41_DEU_shp", "gadm41_DEU_4.shp"))

#filtering for Dresden
dresden <- ger_4  %>% 
  filter(NAME_4=="Dresden")


# to exctract the outliers that located outside the city, when i arranged the apartment_rent data WKT column I saw the coordinate that differ from others to much thats why I exract using filter function
apartment_rent <- apartment_rent %>% 
  filter(!Ort=="DresdenNeustadt")


apar_sf <- st_as_sf(apartment_rent, wkt = "WKT")
st_crs(apar_sf) <- 32633

apar_sf <- st_transform(apar_sf, crs = 4326)



#cropping and masking
dresden_no <- crop(no, dresden )
dresden_no_mask <- mask(dresden_no, dresden )

apar_terra <- vect(apar_sf)
dresden_terra <- vect(dresden)
area_apar <- crop(apar_terra, dresden_terra)
area_apar_sf <- st_as_sf(area_apar)
dresden_sf <- st_as_sf(dresden)


#use disaggregate for perfect vizualitation
dresden_no_mask <- disaggregate(dresden_no_mask, fact=20, method='bilinear')


#convert it to df
dresden_no_mask_df <- as.data.frame(dresden_no_mask, xy = TRUE, na.rm = TRUE)






#apartments in Dresden
apar_area_plot <- ggplot() +
  geom_sf(data = dresden) +
  geom_sf(data = area_apar_sf, aes(fill = "Apartment Rent prices"), colour = "blue") +
  labs(title = "Apartments in Dresden",fill = "") +
  theme_minimal()


# Apartmennts and  NO2 emissions in Dresden
apar_no_area_plot <- ggplot() +
  geom_sf(data = dresden_sf, fill = "grey80") +
  geom_raster(data = dresden_no_mask_df, aes(x = x, y = y, fill = X2015_final_1km)) +
  scale_fill_gradient(low = "yellow", high = "red", name = "Emission Levels") +
  geom_sf(data = area_apar_sf, aes(color = "Apartments"), size = 2, show.legend = "point") +
  scale_color_manual(values = c("Apartments" = "black"), name = "Features") +
  labs(title = "Apartments and Emissions in Dresden", 
       fill = "Emission Levels", 
       color = "Features") +
  theme_minimal()




plot(apar_area_plot)
plot(apar_no_area_plot)
plot(dresden_no_mask)


```
plot(apar_area_plot)
plot(apar_no_area_plot)
plot(dresden_no_mask)








```{r}


# convert the dresden_no_mask_df to  Spatial DataFrame-
dresden_no_mask_sf <- st_as_sf(dresden_no_mask_df, coords = c("x", "y"), crs = 4326)


#same crs
crs(dresden_no_mask_sf)
crs(apar_sf)


# I used the nearest neighbourhud for finding each apartment points nearest emissions

apartment_rent_with_emissions <- st_join(apar_sf, dresden_no_mask_sf, join = st_nearest_feature)


# to look merge data
head(apartment_rent_with_emissions)



```






```{r creating the adress}

hbf <- tibble::tribble(
~name,~addr,
"Dresden Hbf",  "Wiener Platz 4, 01069 Dresden")
hbf

hbf_geocode <- hbf %>%
  geocode(addr, method = 'osm', lat = latitude , long = longitude)


hbf_sf <- st_as_sf(hbf_geocode, coords = c("longitude", "latitude"), crs = 4326)










#looking the apartments , emissions and HBF
apar_no_hbf_area_plot <- ggplot() +
  geom_sf(data = dresden_sf, fill = "grey80") +
  geom_raster(data = dresden_no_mask_df, aes(x = x, y = y, fill = X2015_final_1km)) +
  scale_fill_gradient(low = "yellow", high = "red") +
  geom_sf(data = area_apar_sf, aes(color = "Apartments"), size = 2) +
  geom_sf(data = hbf_sf, aes(color = "Main Station"), size = 5, show.legend = "point") +
  scale_color_manual(values = c("Main Station" = "blue", "Apartments" = "black")) +
  labs(fill = "Emission Levels", color = "Features") +
  guides(color = guide_legend(override.aes = list(size = c(2, 5)))) +
  theme_minimal()

plot(apar_no_hbf_area_plot)

```

plot(apar_no_hbf_area_plot)







```{r calculating the distances to hbf}

hbf_distances <- st_distance(hbf_sf, apar_sf)

print(hbf_distances)
hbf_distances_df <- as.data.frame(hbf_distances)
hbf_distances_df <- as.data.frame(t(hbf_distances_df))

hbf_distances_df$ScoutID <- apartment_rent_with_emissions$ScoutID

apartment_rent_with_emissions_hbf <- left_join(hbf_distances_df, apartment_rent_with_emissions, by="ScoutID")

# in this data set I saw that some variables was same except ScoutID and Datum, for keeping only one I did this code, after this still have same adresses but not same prices or rooms maybe modifyed that is why i kept rest of them in my data
apartment_rent_with_emissions_hbf <- apartment_rent_with_emissions_hbf %>%
  distinct(across(-c(ScoutID, Datum)), .keep_all = TRUE)

#lets convert the m to km 
apartment_rent_with_emissions_hbf$V1 <- apartment_rent_with_emissions_hbf$V1 / 1000


```



```{r calculating the regression}
#1st model just calculate adding all important variables using OLS
model_1 <-  lm(log(Kaltmiete)~log(V1)  + log(Wohnflaech)+ EBK+   Zimmer +Etage+Garten+Barrierefr + Keller + BalkonTerr + Aufzug  +log(X2015_final_1km) ,data=apartment_rent_with_emissions_hbf)


stargazer(model_1, type="text")



#For 2nd model I seperated NO2 variables according to the mean to 2 different level, in this regression I will calculate as factor levels

mean_NO2 <- mean(apartment_rent_with_emissions_hbf$X2015_final_1km, na.rm = TRUE)
mean_NO2 # 10.64627

# NO2_category created
apartment_rent_with_emissions_hbf$NO2_category <- ifelse(apartment_rent_with_emissions_hbf$X2015_final_1km <= mean_NO2, "NO2_Low", "NO2_High")

# NO2_category factoring the levels
apartment_rent_with_emissions_hbf$NO2_category <- factor(apartment_rent_with_emissions_hbf$NO2_category, levels = c("NO2_Low", "NO2_High"))


#model 2
model_2 <-  lm(log(Kaltmiete)~log(V1)  + log(Wohnflaech)+ EBK+  Zimmer +Etage+Garten+Barrierefr + Keller + BalkonTerr + Aufzug  +NO2_category   ,data=apartment_rent_with_emissions_hbf)


stargazer(model_1, model_2, type="text")




```
```{r creating histogram for plotting NO2 level distrubition}


breaks <- c(5, 10.64627, 17)
labels <- c("Low level", "High level")

# Create a new column in the data frame for the bins
apartment_rent_with_emissions_hbf$NO2_bins <- cut(apartment_rent_with_emissions_hbf$X2015_final_1km, breaks = breaks, labels = labels, include.lowest = TRUE, right = FALSE)

# Calculatte the frequencies and percentages
bin_counts <- table(apartment_rent_with_emissions_hbf$NO2_bins)
bin_percentages <- prop.table(bin_counts) * 100

# Convert to data frame for plotting
bin_data <- as.data.frame(bin_counts)
colnames(bin_data) <- c("NO2_bins", "Count")
bin_data$Percentage <- bin_percentages[bin_data$NO2_bins]





```
ggplot(bin_data, aes(x = NO2_bins, y = Count)) +
    geom_bar(stat = "identity", color = "black", fill = "blue") +
    geom_text(aes(label = paste0(round(Percentage, 1), "%")), vjust = -0.5) +
    labs(title = "Distribution of NO2 Levels", x = "NO2 Levels", y = "Frequency") +
    theme_minimal()
    
    
    
```{r creating histogram for rent distrubition}
# Kira aralıkları ve etiketler
breaks <- c(100, 300, 500, 1000, 1500, 2600)
labels <- c("100-300", "300-500", "500-1000", "1000-1500", "1500-2600")

# Kaltmiete sütununu belirtilen aralıklara göre bölen yeni bir sütun oluşturun
apartment_rent_with_emissions_hbf$Kaltmiete_bins <- cut(apartment_rent_with_emissions_hbf$Kaltmiete, breaks = breaks, labels = labels, include.lowest = TRUE, right = FALSE)

# Frekansları ve yüzdeleri hesaplayın
bin_counts <- table(apartment_rent_with_emissions_hbf$Kaltmiete_bins)
bin_percentages <- prop.table(bin_counts) * 100

# Sonuçları grafik için bir veri çerçevesine dönüştürün
bin_data <- as.data.frame(bin_counts)
colnames(bin_data) <- c("Kaltmiete_bins", "Count")
bin_data$Percentage <- bin_percentages[bin_data$Kaltmiete_bins]
```
    
ggplot(bin_data, aes(x = Kaltmiete_bins, y = Count)) +
    geom_bar(stat = "identity", color = "black", fill = "blue") +
    geom_text(aes(label = paste0(round(Percentage, 1), "%")), vjust = -0.5) +
    labs(title = "Distribution of Rent Prices", x = "Rent Prices (Kaltmiete)", y = "Numbers") +
    theme_minimal()